The \dealii Library, Version 9.7

### 2025-07-14 9.7/paper.tex
Add some text for SolutionTransfer.

>>>>

\subsection{The \texttt{SolutionTransfer} class}
This release extends the \texttt{SolutionTransfer} class to support mesh
adaptivity with all \texttt{Triangulation} classes which support refinement.
Consequently, the \texttt{parallel::distributed::Triangulation} class is no
longer necessary to use and is deprecated. Some member functions, such as
\texttt{execute\_pure\_refinement()}, have been removed from the new
implementation.
